Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
part of proof to lemma 3.7

\begin{rem}
Fact about quotient.
\end{rem}

@@

\todo{Peter: We should make the definition of admissibility be a 
condition for the triple: $(\sx',\sx,J)$.}

\begin{enumerate}
	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}\label{lem:n-3s-admissible}
Let $(\sx', L', \Delta), (\sx, L,\Delta)$ be log stacky curve with log half-canonical divisors $L'$ and $L$ with signatures $(g; e_1, \ldots, e_{r-1}; \delta)$ and $(g; e_1, \ldots, e_r; \delta)$ with all $e_i=3$ and $L=L'+\frac{1}{3}P$ for some point $P$.  Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
\end{lem}
\begin{proof}\todo{proof}

\end{proof}

>>>>

\begin{rem}
In particular, in the case of
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
inducing
\[
	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
\]
\todo{how do we make this proof?}
\end{rem}

@@

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number.  What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}\label{lem:n-3s-admissible}
Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.  Suppose $3\le r\in \mathbf{N}$ so that all stacky curves $\sx'$ with $r-1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ admissible in $L'$.  Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i=3$) is admissible viewed in $L$.
\end{lem}
\begin{proof}\todo{proof}
To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r-1$ stacky points $S=\{Q_1, \ldots, Q_{j-1}, Q_{j+1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).  Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).  Furthermore, since $S$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}=0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}

 follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
\begin{itemize}
\item When $g>0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
\item When $g=0$, since $L'$ has a nontrivial admissible subset within $\{e_1,\ldots, e_{r-1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
\end{itemize}
\end{proof}
